preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2020-09-16 Manuscript/manuscript.Rmd
editted suppfig10 and legend

**Supplementary Figure 10.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps). Data from GM12878 and K562 cell lines, chromosome 22, at 5kb resolution was used. NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model. Error bars indicate standard deviation away from the mean.

>>>>

**Supplementary Figure 10.** Linecharts illustrating the normalized enrichment (NE) between known molecular drivers of 3D chromatin and resolution-flanked *preciseTAD*-predicted boundaries for different combinations of thresholds (t) and epsilon parameter values (eps) using data from GM12878 (A) and K562 (B) cell lines, chromosome 22, at 5kb resolution was used. NE was calculated as the total number of ChIP-seq peaks that overlapped within a given flanked boundary, divided by the number of boundaries that were predicted, and averaged over the number of annotations included in the model. Error bars indicate standard deviation away from the mean.
